On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 hamiltonian.tex
Make editorial changes and add TODO on writing

In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{put proofs back. Adiabatic ref?}

\Ethan{Adiabatic and spectral gap ref = \cite{adiabatic}}

First note that $\set{H, T}$ is a universal gate set.

\hannote{citation}
\begin{thm}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
\end{thm}

 We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$.% and define the following that implicitly depends on $L$.

\begin{definition}
	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
\end{definition}

\hannote{something?}

\begin{thm}
	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$. We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}

	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{thm}

\begin{thm}
	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$. In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$. Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
\end{thm}

Lastly, before we present proofs for the above theorems, we make an observation.

\begin{observation}
	\label{idpadding}
	Given a circuit $C$ and an input string $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtaining another circuit $C'$. One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
\end{observation}

@@

\hannote{throw this into appendix?}
 Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set. Because of this result, we cam assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.

@@

\begin{thm}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{thm}

@@

\begin{proof}
	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

@@

	Next, we check that $H_{prop}\geq0$ by the following transform.

	$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
	$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
	$$W^\dagger H_{prop} W=
	\begin{pmatrix}
		\frac{1}{2} & -\frac{1}{2} & & & &  \\
		-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
		& -\frac{1}{2} & 1 & \ddots & & \\
		& & \ddots & \ddots & -\frac{1}{2} & \\
		& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
		& & & & -\frac{1}{2} & \frac{1}{2}
	\end{pmatrix}$$

	According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.

	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
	Extra care must be taken for boundary cases.
	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$

>>>>

In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem.

\Ethan{TODO Give a bit of overview on what is this (I.e. QMA-completeness and whatnot)}

This section will mostly be a summarization of known results related to adiabatic quantum computation found in sources such as \cite{adiabatic}. \Ethan{This source was given to us by Yu-Ching; I haven't read it}

\Ethan{TODO Say something about wanting to do more with $\QMA$ certificates than just check yes/no-instances}

Recall the following form that $\QMA$ certificates take:

\begin{dfn}
	\label{dfn:groundstate}	
	Let $C=U_T\ldots U_1$ be a quantum circuit consisting of $T$ gates, and let $x\in\set{0,1}^n$. Then we denote
	$$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$$
	We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
\end{dfn}

\begin{rmk}
	\label{idpadding}
	One can first pad $C$ with identity gates at the end, doubling its number of gates and obtaining another circuit $C'$.
	Then by measuring the time register of $\ket{\psi_{C'(x)}}$ one obtains with probability $\frac{1}{2}$ the state $C(x)$.
\end{rmk}

\Ethan{Now say something about QMA here...}

We denote the set of $5$-local tensor products of $X$ and $Z$ gates as $\mathcal{G}_{XZ}$. \Ethan{mention it's the basis for 5-local Hamiltonians?}

\begin{dfn}
	$$\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq 5}$$
\end{dfn}

\begin{thm}
	Let $C$ be a circuit of size $T$. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
	\end{itemize}
\end{thm}

\begin{thm}
	Given circuit $C$ and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$. In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$. Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
\end{thm}

@@

\hannote{throw this into appendix?}
Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set.
Because of this result, we can assume without loss of generality that our quantum circuits consists of only Toffoli and Hadamard gates.

@@

\begin{thm}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ and $\Lambda(P(i))$
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{thm}

@@

\begin{proof}
	The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues.

@@

	We have $H_{prop}\geq 0$ according to \cite{2002quant.ph.10077A}; in fact, the least nonzero eigenvalue of $H_{prop}$ is lower bounded by $\frac{1}{2(T+1)^2}$.

	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since our gates are either Hadamard or Toffoli.
	Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
	Extra care must be taken for boundary cases.
	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$

### 2020-02-05 preliminaries.tex
Make editorial changes and add TODO on writing

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

>>>>

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists product of $X$ and $Z$ measurements $\Lambda'$ and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}
